Increasing the topological gap by an order of magnitude through the geomerty for Majorana SNS junctions.

### 2018-11-14 paper/snakemajoranas.tex
add paragraphs (Anton's suggestion)
add bandstructures plot
fix the bandstructure plot

\comment{The gap is small because of long trajectories.}

@@

\begin{figure}
% \includegraphics[width=0.95\columnwidth]{figures/SOME_FIGURE}
\caption{Figure of the bandstuctures.
Where the lines are (blue) $\phi=0$, $B=0$ and (red) $\phi=\pi$, $B \ne 0$.
and the subplots (a) $z_y=0$, (b) $z_y=\frac{W}{2}$, and (c) $z_y=W$, where $W$ is the junction width.
\label{fig:bandstuctures}}
\end{figure}

>>>>

\comment{Majoranas are mostly made in hybrid NS structures.}
\comment{Currently proposed workarounds are low density or disorder, but both have drawbacks.}
\comment{The gap is small because of long trajectories.}
\comment{We show that zigzag geometry solves this problem in a controllable manner.}

@@

\begin{figure}
\includegraphics[width=0.95\columnwidth]{figures/bandstructures}
\caption{Figure of the bandstuctures.
Where the lines are (blue) $\phi=0$, $B=0$ and (red) $\phi=\pi$, $B \ne 0$.
and the subplots (a) $z_y=0$, (b) $z_y=\frac{W}{4}$, and (c) $z_y=\frac{W}{2}$, where $W$ is the junction width.
We observe that once there are no more straight trajectories inside the junction (when $z_y=\frac{W}{2}$) the spectrum becomes most insensitive to the momentum $k_x$.
\label{fig:bandstuctures}}
\end{figure}
